\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[purple]{classic}
\usepackage[utf8]{inputenc}
\usepackage[unicode]{hyperref}

\usepackage{geometry}
\geometry{left=2.0cm}
\geometry{right=1.5cm}
\geometry{top=1.0cm}
\geometry{bottom=1.5cm}

\firstname{Andrey}
\familyname{Morozov}
\address{}{Nizhny Novgorod, Russia}
\mobile{+7 920 065 2775}
\email{morozov.andrey.vmk@gmail.com}
\homepage{https://github.com/aod314/}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\moderncvcolor{green} 

\begin{document}
\maketitle

\section{About}
Cross-functional expert in the field of computer vision algorithms, hardware architecture, project management and QA.

\section{Experience}
\cventry{\textbf{June 2017 - now}}
	{Aquantia RUS}{Nizhny Novgorod, Russia}{}{}
  	{Senior QA engineer}
  	
\cventry{}
	{Autotests}{2017-2018}{}{}
	{Write auto-tests and automation's multi-platform scripts.}
  
\cventry{}
	{Tests for PHY}{2018-2019}{}{}
	{Write complex tests for PHY.}

\cventry{}
	{CI/CD}{2019-2020}{}{}
	{Support and improve existing CI/CD system.}

\cventry{\textbf{Nov 2015 - June 2017}}
	{ANKH-NN}{Nizhny Novgorod, Russia}{}{}
  	{CEO}
  
\cventry{}
	{HighLoad}{Sep 2016 - June 2017}{}{}
	{Design and development web application for highload system}
 
\cventry{\textbf{Sep 2009 - Apr 2016}}
	{Itseez}{Nizhny Novgorod, Russia}{}{}
	{Software Engineer}
  
\cventry{}
	{Continuous Integration}{2010-2011}{}{}
	{Deployed Buildbot for OpenCV project (\url{http://build.opencv.org/buildbot})}

\cventry{}
	{Building}{May 2012 - Sep 2012}{Kamchia, Bulgaria}{}
	{Oversaw the construction of the planetarium.}

\cventry{}
	{2D/3D computer vision}{Sep 2012 - Jan 2014}{} {}
	{Calibrate RGB cameras to calculate depth. Created application for Android. Team management.}

\cventry{}
	{Optimization}{Jan 2014 - Apr 2016}{}{}   
	{Low level optimization of algorithms of OpenCV for custom hardware(DSP)}

\cventry{\textbf{Jun 2005 - May 2010}}
	{School \#91}{Nizhny Novgorod, Russia}{}{}
	{Teacher of additional education. Administrator of computer class.}
  
\section{Education}
  \cventry
    {2005 - 2011}
    {Lobachevsky State University}
    {Nizhny Novgorod, Russia}
    {}{}
    {Faculty of Computational Mathematics and Cybernetics. Department of computer software.\newline{}
    Master's Degree}


\section{Skills}
\cvline  {Languages}{python, c/c++}
\cvline  {OS}{Linux, Windows, macOS}
\cvline  {VCS}{Git}
\cvline  {Tools}{QtCreator, vim, sublime text, cmake, ninja, gcc/clang}
\cvline  {Frameworks}{opencv, tbb, opengl, cuda, opencl, postgresql, pytest}
\cvline  {Development technics}{\textbf{Agile:} TDD, Continuous Integration, XP, Scrum, Lean, Kanban}

\section{Optional skills}
\cvline {Languages}{HTML/JS, SQL, \LaTeX, Rust}

\section{Interests}
\cvline { }{HighLoad, BigData}


\section{Main contribute to OpenSource Projects}
\cvline
  {opencv}
  {\url{https://github.com/itseez/opencv}\newline{}
  Open Source Computer Vision Library (\url{http://opencv.org})}

\cvline
  {mpv}
  {\url{https://github.com/mpv-player/mpv}\newline{}
  Video player based on MPlayer/mplayer2 (\url{http://mpv.io})}

\cvline
  {agile}
  {
  \url{https://github.com/unn-vmk-software/agile-course-theory}\newline{}
  \url{https://github.com/unn-vmk-software/agile-course-practice}\newline{}
  Master course on Agile Development (theory and practice)
  }

\end{document}
